---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# tsextras

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

The goal of tsextras is to provide helper functions to analyse time series objects.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("alberto-mateos-mo/tsextras")
```

## Example

`ts_plot()` function is a wrapper for other functions that plot ts objects.

```{r example}
library(tsextras)
library(ggplot2)

ts_plot(AirPassengers)
```

`ts_trend()` extracts and plots the trend of a time series.

```{r}
library(tsextras)
library(ggplot2)

ts_trend(AirPassengers, order = 12)
```

`ts_season()` extracts and plots seasonal component of a time series.

```{r}
library(tsextras)
library(ggplot2)

s <- AirPassengers
x <- ts_trend(s)
ts_season(x)
```

